Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}

### 2015-04-24 paper.tex
working on related work

\section{Introduction}
% Background information and problem description. What is the general area of research and the specific problem that will be tackled?

One, a Hard Problem in Secure Communication is metadata \cite{hardprob}. Two, usable encryption tools for email is historically hard and still is \cite{johnny}. But https does it just fine. Goal: develop the necessary ecosystem to enable metadata-secure email with no extra effort from the end user.

Give a history of email security/usability/etc. PGP, Why Johnny can't encrypt \cite{johnny}, iMessage, TextSecure and WhatsApp. Introduce the term metadata-secure messaging (MSM).

\section{Related work}
% Related research. Have there been previous academic papers on this or related topics? Are there companies that have developed related software products? What is the historical context? Be sure to cite related research properly. Include a bibliography at the end of your paper.
Many combinations of options exist \cite{spreadsheet}. (Figure out how to cite JB's Summary of Knowledge.)

\subsection{Facebook Message Hannover Study}
What I'm working on for email, but for Facebook. \cite{fahl}

\subsection{Email over Tor}
Tor Mail, OnionMail

\subsection{Mailpile}
Their general ideas, storage solutions. \cite{mailpile}

\subsection{Mailpile SMTorP Plugin}
Explain Tor \cite{tor}, .onion Addresses \cite{smtorp}

\subsection{Pond}
Pond is a system for forward secure asynchronous messaging that does not leak traffic information ``except [to] a global passive attacker." \cite{pond}

@@

\section{Threat Model}
Use trike.

\section{Target User}
\label{targetuser}

\section{Design Goals and Non-Goals}
\label{goals}

Some discussion of the usability issues. Garfinkel et al. \cite{garfinkel} talk about ``How to make secure email easier to use,'' and Ruoti et al. talk about dangers in automatic encryption \cite{ruoti}.

\section{Relevant Email Technologies}
Explain how SMTP and IMAP legacy versions work. Probably with some diagrams!
\subsection{Mail Sending and Transport}
SMTP

\subsection{Mail Retrieval, Storage, and Synchronization}
\subsubsection{POP}
\subsubsection{IMAP}
IMAP uses a command-response model. Commands are either tagged with OK, BAD, or NO, or untagged.

\label{legacyimap}

\section{Architecture and Data Flow}
\label{architecture}
% Have you defined your overall software architecture? -- describe it in detail and justify your design.

As discussed in Section~\ref{goals}, a permissible \project solution must be built to integrate with legacy systems. An MSM MUA will also accept legacy SMTP traffic, and it must appear to the user that all messages, once received, are the same. While the user experience must remain consistent, there are multiple possibilities for architecting a storage system consistent with the storage needs. To architect such a backend, there are several possibilities:

@@

In the \project protocol, a standard IMAP client library is wrapped with a \project module. An MUA then uses the \project module in lieu of a standard IMAP connection agent. This module will perform all necessary functions on behalf of the MUA, including encryption, UID translation, and metadata tracking.
% The \project protocol is 
% The core elements of the \project protocol are 
% \begin{enumerate*}[label=(\itshape\arabic*\upshape)]
% \item an \project module used in lieu of a standard IMAP connection agent in an MUA, and
% \item an index file that is stored as a regular message in a legacy IMAP server. \end{enumerate*}
As further described in later sections, the module ensures that metadata is encrypted along with message contents for all messages to be stored on the IMAP server. It also handles the indexing functions, mapping mailboxes to the messages they complain. This is a significant departure from the legacy system, where mailbox names and contents were exposed to the IMAP server. As such, it shifts the burden of tracking, updating, and syncing changes to the INDEX from the server to the client. When one client updates the INDEX, the IMAP server will see that a message has changed, and inform its other clients in the standard method.

@@

\section{Email Usage Measurements}
To determine various factors such as how often to update and how large a fake message should be, an implementation of \project should measure and dynamically learn these values for actual incoming messages for each particular user. The usage patterns of a typical American college student are as follows.

\subsection{Timing}

\section{Technical Details}

@@

\section{Protecting Metadata}

If a message has been received at the client from a secure source as in Section~\ref{mail-from-secure}, we would like to upload it to the IMAP server so that other \project clients can view it, and to achieve user-facing functionality backwards compatibility. Yet if we push a message to the server immediately upon its receipt, we are leaking the time of message receipt to the server. Thus, we need additional mechanisms for ensuring that a server that stores messages cannot determine when a message arrived.

\subsection{Scheduler: Delivering from IMAP Client to IMAP Server}
The primary mechanism for limiting the amount of data the server can determine regarding message arrival metadata is a scheduling module that determines when a message should be pushed up to or pulled down from the server.

@@

This scheduler receives information from the \project module about its state. Namely, it is informed when a message is received at the client or marked for deletion on the server. Instead of immediately performing this action, the \project module will wait until the next timer tick, when it is called to perform its next scheduled action by its client. At that time, it asks the scheduler whether its next action is an UP or DOWN action. The scheduler considers how often messages are being received and how often scheduled communications happen, and returns an UP or DOWN result to keep overall server growth consistent with actual message receipt and deletion rates. The server will be able to see that an UP or DOWN has been performed on schedule, but will gain no more than one bit of metadata on every timer tick.

To implement this one-bit leakage, \project must either push up or pull down a message on each timer tick, whether or not it is has a message to deliver or a deletion scheduled. This condition is satisfied through artifically constructed messages. A constructed message with contents of a random size chosen from a distribution mirroring that of messages usually sent and received of the user is generated, encrypted and packaged as if it were a legitimate message, saved to a FAKE MESSAGES PSEUDO-mailbox, and sent to the server. On deletion, a message from FAKE MESSAGES is chosen at random and deleted in lieu of a legitimate message. These actions appear identical to the server, since the server will see only updates to the INDEX and the append or delete of a message with subject ENCRYPTED <UNIQUE SUBJECT> and encrypted contents.

Even if the user never deletes a message, the scheduler should still periodically return a DOWN bit, so that the contents of the server do not needlessly continuously grow at a high rate. In the case where deletes never occur, one could imagine a schedule of only pushes, timed such that is it similar to the actual receipt rate, say every 20 minutes. This is an unacceptable rate of checking for mail in a modern system, where periodic updates occur an order of magnitude faster. Additionally, since only one message is pushed every $t$ minutes, messages received in a batch of $k$ would be delayed at least $k*t$ minutes.

% Learning Update Schedules - Exponential backoff?

\label{mixing}
\subsection{Message Mixing}
The scheduling mechanism is necessary but not sufficient to hide message arrival metadata from the server. Assume a user never deletes messages, for simplicity. Assume also that the server is maliciously attempting to track metadata, and notes the upload time of each message. Consider two messages, R and F. R is a real message, and F a fake. Initially, the server cannot distinguish between the two messages. Since R is real, there is a probability $p=0$ that it will be deleted at any point in the future. The goal of the scheduling algorithm is to send messages to the server at an effective rate similar to the rate of actual message receipt, so the server does not grow needlessly. Then, the number of fake messages will remain about constant, $k$. So at each timer tick where a DOWN occurs, a fake message will have probability $p=1/k$ of being deleted. Therefore, the probability that a message is not deleted after $n$ DOWN ticks is $(1-1/k)^n$ (since it must not be deleted at all time ticks), which tends towards 0 as $n$ increases. Thus, a fake message's long-term probability of being deleted is 1. So, after a length of time has passed, any message that was uploaded to the server and has remained there for a long period of time is likely a real message, and the server can therefore merely observe the time it was uploaded.

This analysis does not only apply in the theoretical sense. Assume the user had let the system run in a mode where more fake messages are uploaded than are deleted until it was seeded with 5,000 fake messages. After that point, the user wants to keep the size of the mailbox constant, so for each upload (received message), they delete a message as well. Assume also that they would like to spread new messages to other clients of the server within 10 minutes of its receipt (a conservative estimate). Then they must delete a message every 10 minutes as well, which amounts to 144 deletions a day, 52,560 a year, and 262,800 in a five year period, which we conservatively assume is the length of time a user would like to keep an email account for. So $k=5000$ and $n=262800$, giving a probability of a fake message not being deleted of about $1.5\times10^{-23}$, which is certainly distinguishable from $p=1$ for a real message.

\subsubsection{Hiding Among Many}
We can imagine a solution to this problem where many more fake messages are added than real messages, driving down the probability that a fake message is chosen for deletion until it resembles the probability that a real message is chosen, 0. (Note that even in this case we will still desire scheduled deletions, to disguise deletions of real messages.) Assume for simplicity that fake messages are added at an amortized constant rate. We would like to calculate the probability that a fake message is not deleted after the $n$ DOWN ticks following its upload at time $t$. This is equal to the product of the probabilities that a fake message was not deleted at all ticks between times $t$ and $t+n$. We can compute this based on the probability of deleting a message at a particular time after $i$ deletion intervals. Assume that at each each interval, $c+1$ real messages and $f$ fake messages came in. Then the probability that a message was fake is $f/(c+f+1)$, and $c+f+1$ messages total came in each interval. But one message was deleted each interval, so $c+f$ net messages are added. So after $i$ intervals, $i(c+f)$ messages are in the server total, and an expected $i(c+f)f/(c+f+1)\approx if$ of those are fake. So the probability of a message being deleted at time $i$ given that it is fake is $1/(if)$, and the probability that it is not deleted is $1-1/(if)$. Then if the message was uploaded at time $t$, the probability that it was not deleted at time $n$ is $\displaystyle\prod_{i=t}^{i=t+n}(1-\frac{1}{if})$. This product tends towards 0 as $n$ tends towards infinity, but its slope drops off quickly as $f$ increases.

@@

In this case, we need an $f$ of 64 to achieve merely a $p=0.89$ that a fake message is not deleted (compare, of course, with $p=1$ for a real message under the assumption that no real messages are ever deleted).

Is this feasible? Certainly with no space constraints, it is, but we must also consider this solution under reasonable constraints. Gmail, a popular email provider, allots 17 GB of space to a user. Assume that a user wants to use this email address for 5 years (a conservative estimate), and that messages average 170 kB (this number is accurate for my personal email account). Then, 100,000 messages will fit into the server. Say that we are comfortable with having 32 fake messages uploaded per delete operation. Even discounting other messages received in the mail server, this only allows 3125 delete operations, which amounts to 1.7 delete operations per day over the five years. This amount to a delay of about 7 hours any time the user would like to delete a message \--- and this is not taking into account the space that real messages will use. While a user without space constraints could certainly choose this method, we will now describe a more feasible solution.

\subsubsection{Mixing}
We can achieve metadata security while constraining mail server growth to a rate roughly consistent with the number of received messages. To do this, \project implements a mixing mechanism whereby scheduled updates push and pull not only a single message, but multiple messages among which the true target message will be disguised.

On a scheduled timer tick with action UP, \project selects MIX NUMBER messages from all messages with an entry in the current INDEX, (those being the messages that exist in CRYPTOBLOBS). It then FETCHes those messages from the server, reassigns their UNIQUE SUBJECTs, reuploads the new messages to the server, then deletes the messages that were fetched. When the messages are reuploaded, the new message is randomly inserted in with them, indistinguishable from the other messages. On a DOWN operation, a similar mixing occurs. MIX NUMBER + 1 messages are selected at random. If the message to be deleted is not among them, one of the selected messages is replaced with the message to actually be deleted. \project then fetches all MIX NUMBER + 1 messages, reassigns UNIQUE SUBJECTs, reuploads the MIX NUMBER messages that are not actually marked for deletion, then deletes all chosen messages. If there are fewer than MIX NUMBER messages to choose from, all existing messages are mixed.

>>>>

\section{Introduction}

Communication is important.

Secure communication is important.

Metadata is important.

End to end is important.

Current things are either not for email, not usable, don't handle metadata, or some combination of these.

There are experimental transport protocols, but these are only interchangeable with smtp - need further support for storage, one way to do which is IMAP.

Goals:
backwards compatible from a user perspective
end-to-end metadata security
multi-client (because IMAP)

Garfinkel et al. \cite{garfinkel} talk about ``How to make secure email easier to use,'' and Ruoti et al. talk about dangers in automatic encryption \cite{ruoti}.

\section{Relevant technologies and related work}

\subsection{Classical email}
Modern email is composed of two distinct protocol stages: sending and transport, and storage and retrieval, shown below in a diagram from \cite{smtp_imap}.

\begin{center}
\includegraphics[width=0.6\textwidth]{smtp_imap}
\end{center}

To send an email, the sender's machine send a request to an SMTP server acting on its behalf, which relays it through other SMTP servers until it reaches the recipient's destination server. At that point, the recipient's machine retrieves the email from the server using either POP or IMAP.

\subsubsection{Mail Sending and Transport}
The standard sending and transport protocol is Simple Mail Transfer Protocol (SMTP), first defined in RFC 821 \cite{postel1982rfc} in 1982, and most recently updated in RFC 5321 \cite{klensin2008rfc}. SMTP is an application-layer Internet protocol. In SMTP, a user runs a mail client, or a mail user agent (MUA). This MUA submits mail to a mail server, or a mail submission agent (MSA) on either port 25, 587, or with SSL enabled on 465. The MSA passes the message to a mail transfer agent (MTA), which is often on the same machine as the MSA. The MTA then looks to transfer the message to the recipient's mail exchanger (MX). It does this by looking up the recipient's domain in the Domain name system (DNS). The MTA then sends the email over the Internet to the MX. The MX then sends the email to the recipient's mail delivery agent (MDA). The MDA will either store the message or continue to forward them to another MDA. Upon arriving at their final MDA, the SMTP portion of email delivery is complete.

\label{legacyimap}
\subsubsection{Mail Retrieval, Storage, and Synchronization}
Once a message has arrived at an MDA, the recipient's MUA must retrieve the message. For this, most MUAs use either POP or IMAP. Post Office Protocol (POP) is a simple protocol that enables downloads and deletions, and is most often used when a single client is interested in retrieving mail from an MDA \cite{reynolds1984post}, \cite{myers1996post}. The Internet Message Access Protocol is a more complex protocol that enables multiple clients to be connected to the same mailbox, and has come into more widespread use in recent years \cite{crispin2003internet}.

The current version of IMAP is IMAP 4 revision 1 (IMAP4rev1). An IMAP client connects to an IMAP server over port 143, or over 993 if using SSL. The protocol allows a rich set of commands and actions, enabling clients to create, delete, and rename mailboxes, check for new messages, permanently remove messages, set and clear flags that facilitate multi-client synchronization, and more. Communication is structured in a command-response model, where all messages sent from the server are direct responses to requests from the client. Commands can be tagged with various labels, including OK to indicate success and BAD to indicate a malformed command, or they can be untagged. Many modern languages, including Python, include a library for sending commands to an IMAP server.

\subsection{Non-metadata End-To-End (E2E) Security}
While the standard email protocols are not secure in and of themselves, there have been numerous attempts over the years to provide secure alternatives. Link encryption (sending over SSL/TLS) has been the most widely adopted, but suggestions for messaging with E2E security have been propsed to varying levels of adoption and with a diverse range of feature inclusion \cite{unger2015sok}. These features include synchronicity, deniability and forward/backward secrecy.

\subsubsection{Pretty Good Privacy (PGP)}
PGP is the classic example of an end-to-end email encryption tool, and also the classic example of a usability failure. Defined in RFC 4880 as the OpenPGP standard, it provides users the ability to sign, encrypt, and decrypt data using a combination of symmetric and public key cryptography \cite{callas2007openpgp}. Unfortunately, usability studies continue to find that users of the system are unable to use it properly, with errors ranging from key management issues to the inability to encrypt a message \cite{whitten1999johnny} \cite{sheng2006johnny}. Even for users for whom communication secrecy is vital to operational success, such as people working on sensitive projects at a non-violent, direct action organization, it is still easy to make errors that compromise the security of the emails \cite{gaw2006secrecy}.

\subsubsection{Yahoo! E2E Extension}
In the past year, major mail providers have begun to express public interest in providing E2E encryption for their users. In particular, Yahoo! recently released the source for a browser extension (based on one developed by Google) that modifies the Yahoo! webmail client to integrate E2E \cite{yahooe2e}. It handles key management automatically, decreasing the cognitive load on the user. Since it is developed in-house, it has both the design resources and engineering manpower of a modern large technology company.

\subsubsection{Messaging Apps}
Some of the most usable E2E solutions are not for email, but for mobile chat. Apple's iMessage application encrypts messages E2E, although their key management system is unknown and may therefore be invisibly compromised \cite{imessage}. Yet their messaging system is not only usable, it is a widely-adopted example of a smooth transition to an updated protocol without problematic updates to the user experience.

Signal, WhatsApp, iMessage
\subsection{Facebook Message Hannover Study}
What I'm working on for email, but for Facebook. \cite{fahl}

\subsection{E2E Metadata Security for Transport}
\subsubsection{Mailpile's SMTorP}
Also their general ideas, storage solutions. \cite{mailpile}
Explain Tor \cite{tor}, .onion Addresses \cite{smtorp}
\subsubsection{Pond}
Pond is a system for forward secure asynchronous messaging that does not leak traffic information ``except [to] a global passive attacker." \cite{pond}
\subsubsection{Other}
Tor Mail, OnionMail

@@

\section{Threat model}

\label{targetuser}
\section{Target user}

\section{Design overview}
encrypt, hiding sender information inside the contents, inside a special folder. index, lock messages to handle multiple clients. hide metadata by using a combination of scheduling, mixing, fake decoy messages, and possibly ORAM-like techniques. rollback detection for index and messages. key is passphrase/scrypt kdf with salt.

\section{Email Usage Measurements}
To determine various factors such as how often to update and how large a fake message should be, an implementation of \project should measure and dynamically learn these values for actual incoming messages for each particular user. The usage patterns of the author, an American university student, are as follows.

\subsection{Timing}
time of day / week data, distribution of interarrival times

\label{architecture}
\section{Architecture and Data Flow}
% Have you defined your overall software architecture? -- describe it in detail and justify your design.

A permissible \project solution must be built to integrate with legacy systems. An MSM MUA will also accept legacy SMTP traffic, and it must appear to the user that all messages, once received, are the same. While the user experience must remain consistent, there are multiple possibilities for architecting a storage system consistent with the storage needs. To architect such a backend, there are several possibilities:

@@

In the \project protocol, a standard IMAP client library is wrapped with a \project module. An MUA then uses the \project module in lieu of a standard IMAP connection agent. The \project module will perform all necessary functions on behalf of the MUA, including encryption, UID translation, and metadata tracking. The IMAP server is unmodified.
% The \project protocol is 
% The core elements of the \project protocol are 
% \begin{enumerate*}[label=(\itshape\arabic*\upshape)]
% \item an \project module used in lieu of a standard IMAP connection agent in an MUA, and
% \item an index file that is stored as a regular message in a legacy IMAP server. \end{enumerate*}
As further described in later sections, the module ensures that metadata is encrypted along with message contents for all messages to be stored on the IMAP server. It also handles the indexing functions, mapping mailboxes to the messages they contain. This is a significant departure from the legacy system, where mailbox names and contents were exposed to the IMAP server. As such, it shifts the burden of tracking, updating, and syncing changes to the INDEX from the server to the client. When one client updates the INDEX, the IMAP server will see that a message has changed, and inform its other clients in the standard method.

@@

\section{Implementation Details}

@@

\section{Protecting Metadata}
Once a message has been received at the client, we would like to upload it to the IMAP server for storage. Yet while we can hide the FROM and TO headers easily, we do not want the server to gain timing information about the message. If we upload it immediately, then the server will know that we have received a message at that time. Even worse, modern clients often save sent messages to a Sent Messages folder. If the mail server of the sender and the receiver are colluding, as can easily be the case when both clients are using the same company to provide servers, then the server could easily execute timing attacks by observing two users suspecting to be communicating, and seeing if they upload a message at about the same time. So, we must include a mechanism for hiding this timing metadata from the IMAP server. The solution must not allow the server to recover the timing information, it must not take up extraneous amount of space in the mailbox, and it must allow sufficiently frequent and short exchanges with the server. Additionally, for any of these methods, the deletion of a message from the server must not reveal otherwise hidden information.

\subsection{Mechanisms}
While we can vary particular parameters and algorithms, most rely on two primary components, scheduling and mixing.

@@

Fundamentally, scheduling means that \project performs an action at a predetermined time tick. To better reason about the leakage of information, \project contains a separate scheduler module (shown above) that is informed when a message arrives or is marked for deletion. It thus can reason about the expansion rate of the server. At the scheduled time tick, \project will ask the scheduler what its next action should be. This can be one of three types: UP, DOWN, or NONE. UP means that the server will grow in size by one message, DOWN means that it will shrink by one message, and NONE means that the total server size will remain constant. The trit that it outputs is based on its metadata protection policy, determined in conjunction with the \project module. We separate this functionality into the scheduler because it precisely mirrors the information that the server will receive: whether a message has been pushed up, pulled down, or neither. Thus, the server can gain no more than one trit of data on every time tick.

To implement this one-trit leakage, \project must perform the determined action on each timer tick, whether or not it is has a message to deliver or a deletion scheduled. This condition is satisfied through artifically constructed messages. A constructed message with contents of a random size chosen from a distribution mirroring that of messages usually sent and received of the user is generated, encrypted and packaged as if it were a legitimate message, saved to a FAKE MESSAGES PSEUDO-mailbox, and sent to the server. On deletion, a message from FAKE MESSAGES is chosen at random and deleted in lieu of a legitimate message. Without taking into account any other information, these actions would appear identical to the server whether they were performed on real or fake messages, since the server will see only updates to the INDEX and the append or delete of a message with subject ENCRYPTED <UNIQUE SUBJECT> and encrypted contents. How they appear to the server in the context of all actions performed is the subject of Section~\ref{best-metadata}.

\project also incorporates mixing to better hide metadata. In a single mixing step, MIX NUMBER messages are fetched and deleted from the server, and MIX NUMBER $\pm 1$ messages are pushed back to the server so that a particular message in the former set can be associated with all messages in the latter set with equal probability. Note that for mixing to be effective, all messages included in the mix must be of the same size. Which messages are selected to be a part of the mix depends on the metadata hiding strategy.

\label{best-metadata}
\subsection{Strategies}

The requirements that \project has for operations on messages bear resemblance to those of memory operations in oblivious random access memory (ORAM)\cite{oram}. ORAM assumes a situation where multiple actors (say CPUs) can see memory access and store actions on a shared memory module. It proposes a system of additional memory accesses and locations to shield patterns of which memory locations have been accessed. ORAM techniques and implementations are an active area of research, some with proven lower bounds on additional bandwidth cost \cite{stefanov2013path}.

ORAM makes assumptions that we could perhaps consider relaxing. First, ORAM assumes constant, fixed-size blocks of memory. Messages in a mail server need not be constant size, although any solution that involves mixing will require elements of the mix to all be of the same size. Second, a primary goal of ORAM is to hide correlated memory locations. If messages are not decomposed into fixed-size chunks and all saved into the same pseudo-mailbox, then an individual message is not correlated with any other message. Note that mixing will generally require chunking of messages, and we wish to support multiple pseudo-folders, but locations are not as inherently correlated in all cases as they are when a program is executing on memory locations. Third, mailboxes do not allow store operations in the sense of RAM; IMAP only supports appending to mailboxes. Even under these relaxations, most solutions that do not implement an ORAM-adherent technique will trade off either functionality or security.

\subsubsection{Scheduling, no mixing}
Could we implement a mix-free solution where we only schedule UP and DOWN operations, hiding actual message additions and deletions among many fake ones? In such a situation, future actions should not reveal information about which messages previously pushed were real and which were fake. Particularly, assuming that deletions of fake messages occur much more frequently than deletions of real messages, deletion operations should reveal neither whether the particular message deleted or any other was real. Additionally, message fetches must similarly not reveal information regarding the veracity of that message or any other. Note that this last restriction immediately disqualifies this solution barring additional mechanisms to mask message fetches by any client of the server that attempts to download all real messages. Further, naive fetches would leak information about which messages are grouped together in a single mailbox. We will see that it is not practical to attempt to find such mechanisms, since the rate of growth required to sufficiently mask deletion operations is infeasible.

Consider the trivially incorrect case where server growth roughly mirrors the rate of incoming real messages. We upload two messages to the server, R and F. R is a real message, and F a fake. Initially, the server cannot distinguish between the two messages. Since R is real, there is some user-dependent probability $p$ that it will be deleted at any point in the future. Given the availability of storage, a modern trend of archiving, and that these messages are encrypted, we can assume that $p$ is very small. Since we are looking to have server growth mirror the rate of incoming real messages, the goal of the scheduling algorithm is to send messages to the server at an effective rate similar to the rate of actual message receipt, so the server does not grow needlessly. Then, the number of fake messages will remain about constant, $k$. So at each timer tick where a DOWN occurs, a fake message will have probability $p=1/k$ of being deleted. Therefore, the probability that a message is not deleted after $n$ DOWN ticks is $(1-1/k)^n$ (since it must not be deleted at all time ticks), which tends towards 0 as $n$ increases. Thus, a fake message's long-term probability of being deleted is 1. So, after a length of time has passed, any message that was uploaded to the server and has remained there for a long period of time is likely a real message, and the server can therefore merely observe the time it was uploaded.

This analysis does not only apply in the theoretical sense. Assume the user had let the system run in a mode where more fake messages are uploaded than are deleted until it was seeded with 5,000 fake messages. After that point, the user wants to keep the size of the mailbox constant, so for each upload (received message), they delete a message as well. Assume also that they would like to spread new messages to other clients of the server within 10 minutes of its receipt (a conservative estimate). Then they must delete a message every 10 minutes as well, which amounts to 144 deletions a day, 52,560 a year, and 262,800 in a five year period, which we conservatively assume is the length of time a user would like to keep an email account for. So $k=5000$ and $n=262800$, giving a probability of a fake message not being deleted of about $1.5\times10^{-23}$, which is certainly distinguishable from $p \approx 1$ for a real message.

Now assume instead that we will let the server grow to some extent. By adding more fake messages than real messages, we will drive down the probability that a fake message is chosen for deletion until it resembles the probability that a real message is chosen. How often could we delete messages chosen from the set of all fake messages at random before we lose the ability to hide real messages among the fake ones? Assume for simplicity that fake messages are added at an amortized constant rate. We would like to calculate the probability that a fake message is not deleted after the $n$ DOWN ticks following its upload at time $t$. This is equal to the product of the probabilities that a fake message was not deleted at all ticks between times $t$ and $t+n$. We can compute this based on the probability of deleting a message at a particular time after $i$ deletion intervals. Assume that at each each interval, $c+1$ real messages and $f$ fake messages came in. Then the probability that a message was fake is $f/(c+f+1)$, and $c+f+1$ messages total came in each interval. But one message was deleted each interval, so $c+f$ net messages are added. So after $i$ intervals, $i(c+f)$ messages are in the server total, and an expected $i(c+f)f/(c+f+1)\approx if$ of those are fake. So the probability of a message being deleted at time $i$ given that it is fake is $1/(if)$, and the probability that it is not deleted is $1-1/(if)$. Then if the message was uploaded at time $t$, the probability that it was not deleted at time $n$ is $\displaystyle\prod_{i=t}^{i=t+n}(1-\frac{1}{if})$. This product tends towards 0 as $n$ tends towards infinity, but its slope drops off quickly as $f$ increases.

@@

In this case, we need an $f$ of 64 to achieve merely a $p=0.89$ that a fake message is not deleted (compare, of course, with $p=1$ for a real message under the assumption that no real messages are ever deleted). Thus, to achieve even a relatively feasible probability match, we could delete only 1 in 64 messages.

Is this rate of growth sustainable? Theoretically it is, of course, but not given reasonable expectations of server longevity. Assume we would like to delete a message every 64 messages that were pushed, and that one operation occurs per time tick. The following graph relates message check frequency for varying numbers of clients connected to an IMAP server with time to fill a mailbox. The total mailbox size is Gmail's current size of 17 GB, and an average message is 170 kB.

\includegraphics[width=\textwidth]{server_longevity}

With only two clients, if we wish to check our mail more than once every half hour (both of which are conservative estimates), we would use up the space in three years. To compensate for space costs with, we can introduce mixing operations.

\subsubsection{Mixing with \texorpdfstring{$O(1)$}{O(1)} decoys}

If we wish the growth rate of the server to precisely match the rate of messages to be pushed, we must perform many mixing operations. Intuitively, this is because to grow with the actual rate, each fake message that was in an UP operation must appear in a DOWN operation. Mathematically, assume that the mailbox is seeded with $k-1$ fake messages. Consider again messages R and F, and call MIX NUMBER $m$. This time, R and F were each one of $m + 1$ messages pushed to the server, with R pushed into set A and F pushed into set B. Assume no overlap between A and B, since $m<<n$, the total number of messages. This case is similar to the case of no extraneous growth without mixing assessed above, since we are extremely unlikely to have chosen a message in set B were one of them not fake. More precisely, we have at least a $1/k$ probability of choosing a messaging from set B. For choosing at least one message from set A, though, we have a probability of $q = \frac{{m \choose 1}{n-1 \choose m-1}}{{n \choose m}}$. We have ${n \choose k}$ possible ways of choosing $m$ messages from all $n$, and out of those, if at least one must be in A with size $m$, there are ${m \choose 1}$ ways of choosing from those $m$, with any message of the remaining $n-1$ allowed for the remaining $m-1$ spots. We can simplify $q$ to $\frac{m^2}{n}$.

For a reasonable estimation, assume $n=5000$ and $m=10$. Then, $k$ must be at least 50. But this analysis only applies if the adversary does not know which of the messages are the fake $k$ at every time step. So, how many mixing operations do we require to completely mix all $n$ messages? If we are selecting at random, this is the expected number of operations required to select all $n$ messages in batches of $m$, which is a variation on the coupon collector problem. It is not precisely the coupon collector problem, since we are selecting ten at a time, and therefore one batch cannot contain duplicates of the same message, so there is a slightly higher probability of selecting a new one for later messages in a batch. Thus, we can place a lower bound on the number of mixing operations required to select $n$ messages at $E(n) = n \ln (n) / m$. Using our estimates of $5000$ and 10, this is over 4000 mixing operations. We must pull down and push up a total of $2m$ messages for each operation, so that is $2n\ln (n)$ messages that must be transferred to entirely mix the mailbox regardless of $m$. This is unreasonable to do on a regular basis.

\label{fofn}
\subsubsection{Mixing with \texorpdfstring{$f(n)$}{f(n)} decoys}
With more decoy messages, we could select messages for mixing at random, thereby avoiding issues of distingushing between real and fake messages based on probabilistic distinctions. That is, we could initially seed the server with $f(n)$ messages, and schedule only NONE mixing operations where additional messages appear to neither be pulled nor pushed to the server. Then, real messages will be inserted opportunistically as fake messages are selected for mixes, and real messages to be deleted will appear to be in a randomly selected set. The scheduler will then separately decide when to insert an additional fake message in a mix. This insertion is based only on the number of total messages in the server, which the server itself can observe, so no data is leaked there, either.

What does $f(n)$ need to be to ensure a reasonable rate of selecting a fake message? Again assuming a batch size of $m$, we can compute the probability that a fake message is included in a batch, and thereby compute the expected number of mixes before including a fake message in a batch. Here again we can trade off between $f(n)$, which determines total server size, $m$, which determines bandwidth and speed, and frequency of mixes to achieve equivalent rates of being able to insert a message.

TODO: make graphs showing these tradeoffs

While we could achieve reasonable rates in this way, we assume here that a mix is effective \---- that all messages included in it are of the same size, and that fetching patterns do not reveal further information. Neither of these are the case. For the latter, assume that client A performs a mix. If client B soon after that fetches a message that was output from that mix, the server knows that a message was received. For the former, breaking up messages into correlated chunks will again reveal which messages are real. Bucketing solutions where messages are padded to a variety of sizes might be possible, but since message sizes follow a long tail distribution, will likely waste a good deal of space at the longer end of the spectrum. For both of these reasons, an ORAM-like protocol is needed to ensure full metadata protection.

\subsubsection{ORAM-like protocol}

Is applying an ORAM-like protocol feasible? To do this, larger messages must be broken down into chunks of a set size. With a long tail distribution, this is feasible in most cases. Chunks could easily be tracked inside the INDEX, with each piece being fetched sequentially. Using Path ORAM \cite{stefanov2013path}, for a block size of $\Omega (\log ^2 N)$ bits where $N$ is the total number of blocks, there is a bandwidth cost of $O(\log N)$ blocks, and a required $O(\log N)\omega(1)$ blocks stored on the client. Accessing $O(\log N)$ messages per required desired access is a reasonable cost, particularly relative to the overhead of mixing.

TODO: deal with the problem of making a fetch-delete-append operation indistinguishable from an append operation in the way that ORAM get and reads are indistinguishable.
